\Title

### 2021-07-01 manuscript/content.tex
Slight tweaks to caption and section for window overlap

@@

The amount of overlap between adjacent windows plays an important role in the
performance of the gradient-boosted equivalent sources.
It controls the number of iterations and how often a particular source is used
in the least-squares fitting process.
While the experiments in the previous section showed that 50\% overlap was
sufficient to achieve acceptable interpolation accuracy, we separately studied
the impacts of the amount of window overlap on both accuracy and computation
time.

We performed a similar experiment to one in section~\ref{sec:window_size} but
this time kept the window size fixed to \BoostOverlappingWindowSize{} and
varied the amount of overlap from 0\% to 95\% with a step size of 5\%.
All other experimental procedures remained unchanged.
Figs.~\ref{fig:gradient-boosted-comparison}b and
\ref{fig:gradient-boosted-comparison}d show the RMS error and computation time
required for estimating the source coefficients, respectively, as a function of
the window overlap.

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/gradient-boosted-comparisons.pdf}
    \caption{
        Comparison of the interpolation RMS error and computation time for
        regular least-squares equivalent sources (orange dashed lines) and
        gradient-boosted equivalent sources (blue dots and error bars).
        Both methods used the same source positions (block-averaged sources
        with a relative depth).
        Window sizes are given as a percentage of the survey area (e.g., 100\%
        represents a window with the same area as the survey) and window
        overlap is given as a percentage of the window size
        (an overlap of 50\% means that two adjacent windows
        share an area half of the size of the entire window).
        Computation time refers to the time required to estimate the source
        coefficients and is reported as a ratio between the gradient-boosted
        and the regular equivalent sources.
        For gradient-boosting, the RMS errors and computation times are the
        means (error bars represent 1 standard deviation) of results using
        different seeds for the pseudo-random number generator.
        (a)~RMS error between the target grid and interpolation results and
        (b)~RMS error between the target grid and interpolation results and
        (c)~computation time as a function of window size.
        (d)~computation time as a function of window overlap.
}
    \label{fig:gradient-boosted-comparison}
\end{figure*}

>>>>

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/gradient-boosted-comparisons.pdf}
    \caption{
        Interpolation RMS error (a-b) and relative computation time (c-d) for
        regular least-squares equivalent sources (orange dashed lines) and
        gradient-boosted equivalent sources (blue dots and error bars).
        Window overlap is given as a percentage of the window size (an overlap
        of 50\% means that two adjacent windows share an area half of the size
        of the entire window).
        For gradient-boosting, the RMS errors and computation times are the
        means (error bars are 1 standard deviation) of results using different
        seeds for the pseudo-random number generator.
        Computation time is the ratio between the time required to estimate the
        source coefficients for the gradient-boosted and the regular equivalent
        sources.
}
    \label{fig:gradient-boosted-comparison}
\end{figure*}

@@

The amount of overlap between adjacent windows plays an important role in the
performance of the gradient-boosted equivalent sources.
It controls the number of iterations and how many times a particular source is
used in the least-squares fitting process.
The experiments in the previous section showed that 50\% overlap was
sufficient to achieve acceptable interpolation accuracy.
However, we studied separately the impacts of the amount of window overlap on
both accuracy and computation time.

We performed a similar experiment to one in section~\ref{sec:window_size} but
this time kept the window size fixed to \BoostOverlappingWindowSize{} and
varied the amount of overlap from 0\% to 95\% with a step size of 5\%.
All other experimental procedures remained unchanged.
Fig.~\ref{fig:gradient-boosted-comparison}b shows the RMS error and
Fig.~\ref{fig:gradient-boosted-comparison}d shows the computation time
required for estimating the source coefficients, both as functions of
the window overlap.

@@
